What is disputed on the web?

### 2010-02-02 papers/wicow_claimfinder/modals.tex
Subsection on modal phrases

Modals serve a broad variety of purposes;
we are interested particularly in  {\bf epistemic} modality. Epistemic phrases qualify the
degree to which the claim is known~\cite{Palmer.2001}. Most linguistic scholarship has focused on {\it
possibility} and {\it necessity} as epistemic qualifiers. In
contrast, our interest is in qualifiers that call the claim into
question, as a presumption, speculation, or a questionable
opinion. This can often, but not always done by attributing the claim
to some other person's belief, either implicitly or explicitly. The
author in so doing raises an issue about the truth, or lack of truth
of the claim.

>>>>

Modals serve a broad variety of purposes;
we are interested particularly in  {\bf epistemic} modality. Epistemic phrases qualify the
degree to which the claim is known.~\cite{Palmer.2001} Most linguistic scholarship has focused on {\it
possibility} and {\it necessity} as epistemic qualifiers. In
contrast, our interest is in qualifiers that call the claim into
question, as a presumption, speculation, or a questionable
opinion. This can often, but not always done by attributing the claim
to some other person's belief, either implicitly or explicitly. The
author in so doing raises an issue about the truth, or lack of truth
of the claim.
